How to Stop Useless Refactorings

### 2016-08-14 Manuscript.tex
Updates from ShareLaTeX

\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

@@

\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
\ead{rkrish11@ncsu.edu}
\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
\ead{tim.menzies@gmail.com}
\author{Lucas Layman\textsuperscript{b}}
\ead{ llayman@cese.fraunhofer.org }
\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
\address{\textsuperscript{a}Department of Computer Science, North Carolina State University, Raleigh, NC, USA\\
\textsuperscript{b}Fraunhofer CESE, College Park, USA}
\pagestyle{arabic}

@@

\noindent
%%``Managing people is like herding cats'', says management consultant Watler
%Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
%Programmers can be very intelligent, but very opinionated people whose
%social position within software organizations relies, in part,
%of perceived notions of technical excellence. Hence, it can
%be hard for managers to suggest to programmers that are
%wrong about how they are prioritizing their development effort.

%Consider, for example, the activity of refactoring code based on bad smells.
According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
of introducing errors''.
\end{quote}
Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

@@

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we  use Random Forests\cite{XXX}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{YYY}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task to learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

@@

  \subsection{Relationship to Prior Work }
A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
the five data sets studied here. Also, that prior work had:
\bi
\item
no comparison to any baseline
method from other researchers, whereas this paper compares XTREE's recommendations
with those found by researchers exploring bad smells.
\item
no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
\ei
Further, of this entire paper, the only sections containing material
found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{xxx}.

>>>>

\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
% \usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

@@

\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
\ead{rkrish11@ncsu.edu}
\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
\ead{tim.menzies@gmail.com}
\author{Lucas Layman\textsuperscript{b}}
\ead{ llayman@cese.fraunhofer.org }
\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
\address{\textsuperscript{a}Department of Computer Science, North Carolina State University, Raleigh, NC, USA\\
\textsuperscript{b}Fraunhofer CESE, College Park, USA}
\pagenumbering{arabic}

@@

According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
of introducing errors''.
\end{quote}
Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

@@

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we use Random Forests\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task to learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

@@

  \subsection{Relationship to Prior Work }
A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
the five data sets studied here. Also, that prior work had:
\bi
\item
no comparison to any baseline
method from other researchers, whereas this paper compares XTREE's recommendations
with those found by researchers exploring bad smells.
\item
no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
\ei
Further, of this entire paper, the only sections containing material
found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.
